### 2023-10-30 journal/algorithm-GC.tex
editing Section 3; also had to get rid of cleverref since it is incompatible with journal style

\Function{boolean}{Refresh}{\typ{Node} \var{v}} \Comment{try to append a new block to $\var{v}.\fld{blocks}$}
	\gc{
	\State $T$ \assign\ $\var{v}.\fld{blocks}$\label{refreshReadTGC}
    \State $\var{h}$ \assign\ $\Call{MaxBlock}{T}.\fld{index}+1$ \label{refreshReadMax}
    }
    \State $\var{new}$ \assign\ $\Call{CreateBlock}{\var{v, h}}$ \label{invokeCreateBlockGC}
    \If{\var{new = \nl}} \Return{\tr} \label{addOPGC}
    \Else  
    	\gc{
	    \State $T'$ \assign\ $\Call{AddBlock}{v, T, \var{new}}$\label{refreshABGC}
		\State \Return \Call{CAS}{\var{v}.\fld{blocks}, $T$, $T'$}\label{casGC}
		}
    \EndIf
\EndFunction{Refresh}

@@

\Function{Block}{CreateBlock}{\typ{Node} \var{v}, \typ{int} \var{i}} \linecomment{create new block  to install in \var{v}.\fld{blocks}[\var{i}]}
    \State \hangbox{let \var{new} be a new \typ{Block} with fields\label{initNewBlockGC}
    \gc{
    	\eleft\ \assign\ $\Call{MaxBlock}{\var{v}.\fld{left}.\fld{blocks}}.\fld{index}$\label{createEndLeftGC},\\
    \eright\ \assign\ $\Call{MaxBlock}{\var{v}.\fld{right}.\fld{blocks}}.\fld{index}$,\label{createEndRightGC}
    \fld{index} \assign\ $i$\label{createIndexGC}
    }\\
	\fld{sum\sub{enq}} \assign\ \var{v}.\fld{left.blocks}[\var{new}.\eleft].\fld{sum\sub{enq}} + 
			\var{v}.\fld{right.blocks}[\var{new}.\eright].\fld{sum\sub{enq}}\\
	\fld{sum\sub{deq}} \assign\ \var{v}.\fld{left.blocks}[\var{new}.\eleft].\fld{sum\sub{deq}} +
			\var{v}.\fld{right.blocks}[\var{new}.\eright].\fld{sum\sub{deq}}}
    \State \var{num\sub{enq}} \assign\ $\var{new}.\fld{sum\sub{enq}} - \var{v}.\fld{blocks}[\var{i}-1].\fld{sum\sub{enq}}$\label{computeNumEnqGC}
    \State \var{num\sub{deq}} \assign\ $\var{new}.\fld{sum\sub{deq}} - \var{v}.\fld{blocks}[\var{i}-1].\fld{sum\sub{deq}}$
    \If{$\var{v} = \var{root}$} \var{new}.\fld{size} \assign\ max(0, $\var{v}.\fld{blocks}[\var{i}-1].\size\ + 
        	\var{num\sub{enq}} - \var{num\sub{deq}}$)\label{computeLengthGC}
    \EndIf
    \If{$\var{num\sub{enq}} + \var{num\sub{deq}} = 0$} \Return \nl \hfill \Comment{no blocks need to be propagated to \var{v}}\label{testEmptyGC}\label{CBnullGC}
    \Else\ \Return \var{new}
    \EndIf
\EndFunction{CreateBlock}

>>>>

\Function{boolean}{Refresh}{\typ{Node} \var{v}} \Comment{try to append a new block $B$ to $\var{v}.\fld{blocks}$}
	\gc{
	\State $T$ \assign\ $\var{v}.\fld{blocks}$\label{refreshReadTGC}
    \State $\var{h}$ \assign\ $\Call{MaxBlock}{T}.\fld{index}+1$ \label{refreshReadMax}
    }
    \State $\var{B}$ \assign\ $\Call{CreateBlock}{\var{v, h}}$ \label{invokeCreateBlockGC}
    \If{\var{B = \nl}} \Return{\tr} \label{addOPGC}
    \Else  
    	\gc{
	    \State $T'$ \assign\ $\Call{AddBlock}{v, T, \var{B}}$\label{refreshABGC}
		\State \Return \Call{CAS}{\var{v}.\fld{blocks}, $T$, $T'$}\label{casGC}
		}
    \EndIf
\EndFunction{Refresh}

@@

\Function{Block}{CreateBlock}{\typ{Node} \var{v}, \typ{int} \var{i}} \linecomment{create new block $B$ to install in \var{v}.\fld{blocks}[\var{i}]}
    \State \hangbox{let \var{B} be a new \typ{Block} with fields\label{initNewBlockGC}
    \gc{
    	\eleft\ \assign\ $\Call{MaxBlock}{\var{v}.\fld{left}.\fld{blocks}}.\fld{index}$\label{createEndLeftGC},\\
    \eright\ \assign\ $\Call{MaxBlock}{\var{v}.\fld{right}.\fld{blocks}}.\fld{index}$,\label{createEndRightGC}
    \fld{index} \assign\ $i$\label{createIndexGC}
    }\\
	\fld{sum\sub{enq}} \assign\ \var{v}.\fld{left.blocks}[\var{B}.\eleft].\fld{sum\sub{enq}} + 
			\var{v}.\fld{right.blocks}[\var{B}.\eright].\fld{sum\sub{enq}}\\
	\fld{sum\sub{deq}} \assign\ \var{v}.\fld{left.blocks}[\var{B}.\eleft].\fld{sum\sub{deq}} +
			\var{v}.\fld{right.blocks}[\var{B}.\eright].\fld{sum\sub{deq}}}
    \State \var{num\sub{enq}} \assign\ $\var{B}.\fld{sum\sub{enq}} - \var{v}.\fld{blocks}[\var{i}-1].\fld{sum\sub{enq}}$\label{computeNumEnqGC}
    \State \var{num\sub{deq}} \assign\ $\var{B}.\fld{sum\sub{deq}} - \var{v}.\fld{blocks}[\var{i}-1].\fld{sum\sub{deq}}$
    \If{$\var{v} = \var{root}$} \var{B}.\fld{size} \assign\ max(0, $\var{v}.\fld{blocks}[\var{i}-1].\size\ + 
        	\var{num\sub{enq}} - \var{num\sub{deq}}$)\label{computeLengthGC}
    \EndIf
    \If{$\var{num\sub{enq}} + \var{num\sub{deq}} = 0$} \Return \nl \hfill \Comment{no blocks need to be propagated to \var{v}}\label{testEmptyGC}\label{CBnullGC}
    \Else\ \Return \var{B}
    \EndIf
\EndFunction{CreateBlock}
